\documentclass[11pt]{article}

%Deutsche Umlaute als utf-8 Zeichen eingeben:
% \usepackage[utf8]{inputenc}  % <-- für Linux
% Die Abhängigkeit vom Betriebssystem gilt aber nur für den Editor.
% Die LaTeX-Datei wird weiterhin auf jeder Plattform korrekt übersetzt!
% z.B.: äöüß ÄÖÜ
%\usepackage[latin1]{inputenc}
\usepackage[utf8]{inputenc}

%\pagestyle{empty}

\topmargin      = 0in
\oddsidemargin  = 0in
\evensidemargin = 0in
\textwidth  = 6.5in
\textheight = 9in  % 8,8in
\headheight = 0in
\headsep    = 0in  % 0.2in
%\footskip   = 0in
\parindent=0pt
\parsep=0pt

% Packages
\usepackage{amssymb}

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{center}

\begin{tabular}{ll}
		&{\large \bf Wolfgang Tichy}\\\\
Address:	& Science \& Engineering Building, Room 444 \\
		& Physics Department\\
		& Florida Atlantic University\\
		& 777 Glades Road\\
		& Boca Raton, FL 33431\\\\

Phone:		& (561) 318 0442\\
Fax:		& (561) 297 2662\\

E-Mail:		& wolf@fau.edu \\

Homepage: 	& http://www.physics.fau.edu/$\tilde{\ }$wolf \\


\end{tabular}

\end{center}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip
{\bf Education:}\\

\begin{tabular}{ll}
{2001}&  Ph.D. in Physics, Cornell University,
	  Ithaca, NY, USA \\
%{\bf 1999}&  M.S. in Physics, Cornell University,
%	   Ithaca, NY, USA \\
%		& \\
{1996}&  Diplom in Physik, Universit\"at Karlsruhe,
	   Karlsruhe\\ 
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip

{\bf Appointments and professional Training:}\\

\begin{tabular}{ll}
{2014-date}	& Professor of Physics,
		  {Physics Department}\\
		& {Florida Atlantic University (FAU),}
		  {Boca Raton, FL 33431, USA}\\

{2010-2014}	& Associate Professor of Physics,
		  {Physics Department}\\
		& {Florida Atlantic University (FAU),}
		  {Boca Raton, FL 33431, USA}\\

{2005-2010}	& Assistant Professor of Physics,
		  {Physics Department}\\
		& {Florida Atlantic University (FAU),}
		  {Boca Raton, FL 33431, USA}\\

\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%\vspace{0.3in}
%
%{\bf Course Work:}
%
%\vspace{0.25cm}
%In addition to standard graduate courses in Physics, I have also taken
%the following more advanced classes.
%
%\vspace{0.25cm}
%
%\begin{tabular}{lll}
%
%\underline{Physics} & \underline{Astronomy } & 
% \underline{Mathematics} \\
%& & \\
%Quantum Field Theory  & Cosmology         & Physics and Modern Geometry \\
%General Relativity    & Compact Objects   & Mathematical Methods in Physics\\
%Computational Physics & Galactic Structure& \\
%Gravitational Waves   & Stellar Structure & \\
%Statistical Physics   &                   & \\
%
%\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip
%\bigskip
%\clearpage

{\bf Research Interests:}

\begin{itemize}
\item	Numerical simulation of black holes and
	neutron stars, using finite difference or pseudo spectral methods
\item	Binary systems as sources of gravitational waves
\item	Construction of realistic initial data for
	black holes and neutron stars
\item	Post-Newtonian initial data for black holes
%\item	Orbits around black holes when radiation reaction
%	is taken into account
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\medskip
%\bigskip

{\bf Publications since 2009:}\\

T. Dietrich, S. Bernuzzi, M. Ujevic, \underline{W. Tichy},
``Gravitational waves and mass ejecta from binary neutron star mergers:
Effect of the stars' rotation'',
%Phys. Rev. {\bf D??}, 1?????, 2017,
arXiv:1611.07367 [gr-qc]
\\

\underline{W. Tichy},
``The initial value problem as it relates to numerical relativity'',
Rept. Prog. Phys. {\bf 80}, 026901, 2017,
arXiv:1610.03805 [gr-qc]
\\

T. Dietrich, M. Ujevic, \underline{W. Tichy}, S. Bernuzzi, B. Bruegmann,
``Gravitational waves and mass ejecta from binary neutron star mergers:
Effect of the mass-ratio'',
Phys. Rev. {\bf D95}, 024029, 2017,     
arXiv:1607.06636 [gr-qc]
\\

T. Dietrich, N. Moldenhauer, N. K. Johnson-McDaniel, S. Bernuzzi,
C. M. Markakis, B. Bruegmann, \underline{W. Tichy},
``Binary Neutron Stars with Generic Spin, Eccentricity, Mass ratio, and       
Compactness - Quasi-equilibrium Sequences and First Evolutions'',
Phys. Rev. {\bf D92}, 124007, 2015,
arXiv:1507.07100 [gr-qc]
\\

\underline{W. Tichy}, J. R. McDonald, W. A. Miller,
``New efficient algorithm for the isometric embedding of
2-surface metrics in 3 dimensional Euclidean space'',
Class. Quantum Grav. {\bf 32}, 015002 (2015),
arXiv:1411.0975 [gr-qc]
\\

N. Moldenhauer, C. M. Markakis, N. K. Johnson-McDaniel,
\underline{W. Tichy}, B. Bruegmann,
``Initial data for binary neutron stars with adjustable eccentricity'',
Phys. Rev. {\bf D90}, 084043, 2014,
arXiv:1408.4136 [gr-qc]
\\

J. Aasi et al., \underline{W. Tichy} [co-author],
``The NINJA-2 project: Detecting and characterizing gravitational waveforms
modelled using numerical binary black hole simulations'',
Class. Quantum Grav. {\bf 31}, 115004 (2014),
arXiv:1401.0939 [gr-qc]
\\

S. Bernuzzi, T. Dietrich, \underline{W. Tichy}, B. Bruegmann,
``Mergers of binary neutron stars with realistic spin'',
Phys. Rev. {\bf D89}, 104021, 2014,
arXiv:1311.4443 [gr-qc]
\\

I. Hinder, A. Buonanno, M. Boyle, Z. B. Etienne, J. Healy,
N. K. Johnson-McDaniel, A. Nagar, H. Nakano, Y. Pan, H. P. Pfeiffer,
M. Pürrer, C. Reisswig, M. A. Scheel, E. Schnetter, U. Sperhake,
B. Szilágyi, \underline{W. Tichy}, B. Wardell, A. Zenginoglu, D. Alic,
S. Bernuzzi, T. Bode, B. Brügmann, L. T. Buchman, M. Campanelli,
T. Chu, T. Damour, J. D. Grigsby, M. Hannam, R. Haas, D. A. Hemberger,
S. Husa, L. E. Kidder, P. Laguna, L. London, G. Lovelace, C. O. Lousto,
P. Marronetti, R. A. Matzner, P. Mösta, A. Mroué, D. Müller, B. C. Mundim,
A. Nerozzi, V. Paschalidis, D. Pollney, G. Reifenberger, L. Rezzolla,
S. L. Shapiro, D. Shoemaker, A. Taracchini, N. W. Taylor, S. A. Teukolsky,
M. Thierfelder, H. Witek, Y. Zlochower,
``Error-analysis and comparison to analytical models of numerical waveforms
produced by the NRAR Collaboration'',
Class. Quantum Grav. {\bf 31}, 025012 (2013), arXiv:1307.5307 [gr-qc]
\\

P Ajith, Michael Boyle, Duncan A Brown, Bernd Brügmann, Luisa T Buchman,
Laura Cadonati, Manuela Campanelli, Tony Chu, Zachariah B Etienne,
Stephen Fairhurst, Mark Hannam, James Healy, Ian Hinder, Sascha Husa,
Lawrence E Kidder, Badri Krishnan, Pablo Laguna, Yuk Tung Liu, Lionel London,
Carlos O Lousto, Geoffrey Lovelace, Ilana MacDonald, Pedro Marronetti,
Satya Mohapatra, Philipp Mösta, Doreen Müller, Bruno C Mundim,
Hiroyuki Nakano, Frank Ohme, Vasileios Paschalidis, Larne Pekowsky,
Denis Pollney, Harald P Pfeiffer, Marcelo Ponce, Michael Pürrer,
George Reifenberger, Christian Reisswig, Lucía Santamaría, Mark A Scheel,
Stuart L Shapiro, Deirdre Shoemaker, Carlos F Sopuerta, Ulrich Sperhake,
Béla Szilágyi, Nicholas W Taylor, Wolfgang Tichy,
Petr Tsatsin and Yosef Zlochower,
``Addendum to "The NINJA-2 catalog of hybrid
post-Newtonian/numerical-relativity waveforms for non-precessing black-hole
binaries"'',
Class. Quantum Grav. {\bf 30}, 199401 (2013)
\\

D. Hilditch, S. Bernuzzi, M. Thierfelder, Z. Cao,
\underline{W. Tichy}, B. Bruegmann,
``Compact binary evolutions with the Z4c formulation'',
Phys. Rev. {\bf D88},  084057, 2013,
arXiv:1212.2901 [gr-qc]
\\

\underline{W. Tichy},
``Constructing quasi-equilibrium initial data for binary neutron stars
with arbitrary spins'', Phys. Rev. {\bf D86}, 064024, 2012,
arXiv:1209.5336 [gr-qc]
\\

G. Reifenberger and \underline{W. Tichy},
``Alternatives to standard puncture initial data for binary black hole
evolution'', Phys. Rev. {\bf D86}, 064003, 2012,
arXiv:1205.5502 [gr-qc]
\\

%P. Ajith, Michael Boyle, Duncan A. Brown, Bernd Brügmann, Luisa T. Buchman,
%Laura Cadonati, Manuela Campanelli, Tony Chu, Zachariah B. Etienne, Stephen
%Fairhurst, Mark Hannam, James Healy, Ian Hinder, Sascha Husa, Lawrence E.
%Kidder, Badri Krishnan, Pablo Laguna, Yuk Tung Liu, Lionel London, Carlos O.
%Lousto, Geoffrey Lovelace, Ilana MacDonald, Pedro Marronetti, Satya
%Mohapatra, Philipp Mösta, Doreen Müller, Bruno C. Mundim, Hiroyuki Nakano,
%Frank Ohme, Vasileios Paschalidis, Larne Pekowsky, Denis Pollney, Harald P.
%Pfeiffer, Marcelo Ponce, Michael Pürrer, George Reifenberger, Christian
%Reisswig, Lucía Santamaría, Mark A. Scheel, Stuart L. Shapiro, Deirdre
%Shoemaker, Carlos F. Sopuerta, Ulrich Sperhake, Béla Szilágyi, Nicholas W.
%Taylor, Wolfgang Tichy,
%Petr Tsatsin, Yosef Zlochower
P. Ajith et al., \underline{W. Tichy} [co-author],
``The NINJA-2 catalog of hybrid post-Newtonian/numerical-relativity
waveforms for non-precessing black-hole binaries'',
Class. Quant. Grav. {\bf 29}, 124001 (2012), arXiv:1201.5319 [gr-qc]
\\

P. Marronetti and \underline{W. Tichy},
``Recent Advances in the Numerical Simulations of Binary Black Holes'',
Proceedings of the Department of Energy SciDAC Workshop (2011),
arXiv:1107.3703 [gr-qc]
\\

\underline{W. Tichy},
``Initial data for binary neutron stars with arbitrary spins '',
Phys. Rev. {\bf D84}, 024041, 2011,
arXiv:1107.1440 [gr-qc] 
\\

\underline{W. Tichy} and \'E. \'E. Flanagan,
``Covariant formulation of the post-1-Newtonian approximation to General
Relativity'', Phys. Rev. {\bf D 84}, 044038, 2011,
arXiv:1101.0588v1 [gr-qc]
\\

\underline{W. Tichy} and P. Marronetti,
``A Simple method to set up low eccentricity initial data for moving
puncture simulations'', Phys. Rev. {\bf D 83}, 024012, 2011,
arXiv:1010.2936v2 [gr-qc]
\\

B. J. Kelly, \underline{W. Tichy}, Y. Zlochower, M. Campanelli, B. F. Whiting, 
``Post-Newtonian Initial Data with Waves: Progress in Evolution'',
Class. Quant. Grav. {\bf 27}, 114005, 2010,  arXiv:0912.5311 [gr-qc]
\\

N. K. Johnson-McDaniel, N. Yunes, \underline{W. Tichy}, and B. J. Owen,
``Conformally curved binary black hole initial data including tidal
deformations and outgoing radiation'',
Phys. Rev. {\bf D 80}, 124039, 2009, arXiv:0907.0891 [gr-qc]
\\

\underline{W. Tichy},
``Long term black hole evolution with the BSSN system
by pseudo-spectral methods'',
Phys. Rev. {\bf D 80}, 104034, 2009, arXiv:0911.0973v2 [gr-qc] 
\\

I. Vega, S. Detweiler, P. Diener, and \underline{W. Tichy},
``Self-force with (3+1) codes: a primer for numerical relativists'',
Phys. Rev. {\bf D 80}, 084021, 2009, arXiv:0908.2138 [gr-qc]
\\

\underline{W. Tichy},
``A new numerical method to construct binary neutron star initial data'',
Class. Quant. Grav. {\bf 26}, 175018 (2009), arXiv:0908.0620 [gr-qc]
\\

% B. Aylott, J. G. Baker, W. D. Boggs, M. Boyle,
% P. R. Brady, D. A. Brown, B. Brügmann, L. T. Buchman,
% A. Buonanno, L. Cadonati, J. Camp, M. Campanelli, J. Centrella,
% S. Chatterji, N. Christensen, T. Chu, P. Diener, N. Dorband,
% Z. B. Etienne, J. Faber, S. Fairhurst, B. Farr,
% S. Fischetti, G. Guidi, L. M. Goggin, M. Hannam, 
% F. Herrmann, I. Hinder, S. Husa, V. Kalogera, D. Keppel,
% L. E. Kidder, B. J. Kelly, B. Krishnan, P. Laguna, C. O. Lousto,
% I. Mandel, P. Marronetti, R. Matzner, S. T. McWilliams,
% K. D. Matthews, R. Adam Mercer, S. R. P. Mohapatra, A. H. Mroué,
% H. Nakano, E. Ochsner, Y. Pan, L. Pekowsky,
% H. P. Pfeiffer, D. Pollney, F. Pretorius, V. Raymond,
% C. Reisswig, L. Rezzolla, O. Rinne, C. Robinson,
% C. Röver, L. Santamaría, B. Sathyaprakash, M. A. Scheel,
% E. Schnetter, J. Seiler, S. L. Shapiro, D. Shoemaker,
% U. Sperhake, A. Stroeer, R. Sturani, \underline{W. Tichy}, Y.
% T. Liu, M. van der Sluys, J. R. van Meter, R. Vaulin,
% A. Vecchio, J. Veitch, A. Viceré, J. T. Whelan, Y. Zlochower,
B. Aylott et al., \underline{W. Tichy} [co-author],
``Testing gravitational-wave searches with numerical relativity waveforms:
Results from the first Numerical INJection Analysis (NINJA) project'',
Class. Quant. Grav. {\bf 26}, 165008 (2009), arXiv:0901.4399 [gr-qc]
\\

L. Cadonati et al., \underline{W. Tichy} [co-author],
``Status of NINJA: the Numerical INJection Analysis project'',
Class. Quant. Grav. {\bf 26}, 114008 (2009), arXiv:0905.4227 [gr-qc]
\\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip

\bigskip  
\bigskip  
\bigskip  
\bigskip  


{\bf Grants received:}

\begin{itemize}
\item	NSF Gravitation (PHY-1305387)\\
	Studies of General Relativistic Compact-Object Binaries\\
	Award: \$126000, 09/01/2013-08/31/2017\\
	PI: W. Tichy (FAU)
\item	NSF Gravitation (PHY-1204334)\\
	General Relativistic Simulations of binary compact Objects\\
	Award: \$30000, 05/01/2012-04/30/2014\\
	PI: W. Tichy (FAU)
\item	NSF Gravitation (PHY-0855315)\\
	Numerical Studies of Compact-Object Binaries\\
	Award: \$200000, 08/01/2009-07/31/2013\\
	PI: W. Tichy (FAU)
\item	NSF Gravitation (PHY-0652874)\\
	Numerical studies of binary black hole dynamics and waveforms\\
	Award \$120000, 08/01/2007-07/31/2009\\
	PI: W. Tichy (FAU), Co-PI: P. Marronetti (FAU)
\item	NSF Gravitation (PHY-0555644)\\
	Orbiting binary black holes\\
	Award: \$60000, 08/01/2006-07/31/2007\\
	PI: W. Tichy (FAU), Co-PI: P. Marronetti (FAU)
\item	XSEDE Allocation Account (PHY140019)\\
	Spinning Binary Neutron Star Simulations\\
	Computer time: 2898515 SU, 04/01/2014-03/31/2016\\
	PI: W. Tichy (FAU)
\item	XSEDE Allocation Account (TG-PHY140017)\\
	Simulations of binary neutron stars and black holes\\
	Computer time: 150000 SU, 12/20/2013-12/19/2014\\
	PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY100051)\\
	Binary Black Hole Simulations:
	Creation of a public Gravitational Wave Repository at FAU\\
	Computer time: 2500000 SU, 10/01/2010-9/30/2011\\
	PI: P. Marronetti (FAU), Co-PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY090095)\\
	Simulations of binary black holes\\
	Computer time: 200000 SU, 06/10/2009-06/09/2010\\
	PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY080019)\\
	Binary Black Hole Simulations\\
	Computer time: 30000 SU, 02/01/2008-01/31/2009\\
	PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY060052)\\
	Orbiting Black Holes\\
	Computer time: 30000 SU, 09/08/2006-09/30/2007\\
	PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY050012)\\
	Constructing astrophysically realistic binary black hole initial data\\
	Computer time: 30000 SU, 01/2005-01/2006\\
	PI: W. Tichy (FAU)
\item	NCSA Teragrid Allocation Account (PHY050018)\\
	Relativistic Astrophysics: Compact-Object Binaries\\
	Computer time: 105000 SU, 05/01/2005-04/30/2006\\
	PI: P. Marronetti (FAU), Co-PI: W. Tichy (FAU)
\end{itemize}




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip
%\bigskip
%\clearpage

{\bf Invited Talks since 2009:}

\begin{list}{}{\leftmargin=5em \labelsep=1.5em \rightmargin=-8em \labelwidth=7em}
\item[03/2017]	``General Relativistic simulations of neutron stars''\\
		{Physics Seminar}, \\
		{Wichita State University, Wichita, KS}
\item[12/2016]	``Neutron stars, black holes and gravitational waves''\\
		{Presentation about research to high school students}, \\
		{FAU High School, Boca Raton, FL}
\item[03/2016]	``Einstein's Legacy: Black Holes and Gravitational Waves''\\
		{$MA\Theta$ lecture to high school students},\\
		{Florida Atlantic University, Davie, FL}
\item[02/2016]	``Einstein's Legacy: Black Holes and Gravitational Waves''\\
		{Special Frontiers in Science Lecture},\\
		{Florida Atlantic University, Boca Raton, FL}
\item[05/2015]	``Numerical simulations of binary neutron stars with spin''\\
		{Graduiertenkolleg Quantum and Gravitational Fields},\\
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\item[05/2015]	``Isometric embedding of 2-metrics in $\mathbb{R}^3$
		  and some comments on quasi-local mass''\\
		{Physikalisch-Astronomische Fakult\"at},
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\item[02/2014]	``Numerical Relativity''\\
		{Sunshine State Education \& Research Computing Alliance
		summit},\\
		{Florida Atlantic University, Boca Raton, FL}
\item[07/2013]	``Binary black hole evolutions with improved initial data''\\
		{Physikalisch-Astronomische Fakult\"at},
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\item[05/2013]	``General Relativistic simulations of compact binaries''\\
		{Department of Physics and Atmospheric Science},
		{Dalhousie University, Halifax,\\}
		 Canada
\item[03/2013]	``Constructing initial data for binary neutron stars with 
		spins''\\
		{Department of Mathematics},
		{Harvard University, Cambridge MA}
\item[11/2012]	``Simulations of compact-object binaries''\\
		{Department of Physics},
		{Florida Atlantic University, Boca Raton, FL}
\item[07/2012]	``Neutron star binaries with spin''\\
		{Physikalisch-Astronomische Fakult\"at},
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\item[11/2011]	``Initial data for spinning binary neutron stars''\\
		{Department of Physics},
		{University of Florida, Gainesville, FL}
\item[11/2011]	``Binary neutron stars with spin''\\
		{Department of Physics},
		{Florida Atlantic University, Boca Raton, FL}
\item[07/2010]	``Long term black hole evolutions with the BSSN system by
		pseudospectral methods''\\
		{Physikalisch-Astronomische Fakult\"at},
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\item[08/2009]	``Neutron star initial data''\\
		{Physikalisch-Astronomische Fakult\"at},
		{Friedrich-Schiller-Universit\"at Jena, Germany}
\end{list}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
%\clearpage
\bigskip
%%\bigskip

{\bf Talks given at International Conferences since 2009:}

\begin{list}{}{\leftmargin=5em \labelsep=1.5em \rightmargin=-8em \labelwidth=7em}
\item[04/2015] ``Simulations of binary neutron stars with reduced
		 eccentricity''\\
		{APS April Meeting, Baltimore, MD}
\item[04/2014] ``Binary neutron stars with realistic spin''\\
		{APS April Meeting, Savannah, GA}
\item[04/2012] ``Binary neutron stars with spin''\\
		{APS April Meeting, Atlanta, GA}
\item[05/2011] ``Binary neutron star initial data with spin''\\
		{APS April Meeting, Anaheim, CA}
\item[05/2011] ``Initial data for binary neutron stars with arbitrary spin''\\
                {Gulf Gravity Meeting 2011},
		{Florida Atlantic University, Boca Raton, FL}
\item[05/2009] ``A new numerical method for the construction of binary
		neutron star initial data''\\
		{APS April Meeting, Denver, CO}
\end{list}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\clearpage
%\bigskip
\bigskip

{\bf Teaching Experience:}

\begin{list}{}{\leftmargin=6em \labelsep=1.5em \rightmargin=-8em \labelwidth=9em}
\item[since 2005]	Lectures at Florida Atlantic University (FAU):
\\
		Undergraduate Level:
		General Physics I (2009), Intermediate Mechanics (2006),\\
		Undergraduate Research (2014)
\\
		Graduate Level:
		Mechanics (2009-2013), Quantum Mechanics I \& II (2005-2014),\\
		General Relativity (2011,2016), Numerical Relativity (2014,2017)
\item[ 1996-2000]	Teaching assistent at Cornell University:\\
		Honors Physics Sequence: Modern Physics, Quantum Mechanics\\
		Engineering Physics Sequence: Mechanics,
		Optics, Waves and Particles \\
		Non-Major Sequence: Fundamentals of Physics, 
		General Physics 
\item[1995-1996]	Tutor in Physik an der Universität Karlsruhe:\\
	Quantenmechanik, Klassische Mechanik
\end{list}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
%\bigskip

{\bf Other Science related Activities:}

\begin{itemize}
\item	Co-developed and refined the BAM code for the numerical 
	simulation of the Einstein Equations
\item	Developed the SGRID code to simulate the Einstein Equations using
	pseudo-spectral	methods
\item	Member of the Florida Atlantic University SpaceTime (FAUST) group
\item	Member of the American Physical Society (APS)
\item	Collaboration with Bernd Br\"ugmann at Friedrich-Schiller-Universit\"at 
	Jena on binary black hole and neutron star evolutions,
	as well as BAM code development
%\item	Collaboration with Steven Detweiler and Ian Vega at University of Florida
%	(Gainesville) on self-force computations
%\item	Collaboration with Benjamin Owen, Nathan Johnson-McDaniel and
%	Nico Yunes at Penn State University on binary black hole
%	initial data
%\item	Member in the LA Grid (Latin American Grid) Research Community
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
%\bigskip

{\bf Service:}

\begin{itemize}
\item	Referee for the following journals:\\
	Physical Review Letters, Physical Review D,
	Classical \& Quantum Gravity
\item	External Reviewer of NSF proposals in Gravity Theory Program
\item	Member of the 2012 NSF Computational Physics Program panel
\item	Chairman of session on
	``Numerical Analysis of Black Hole Binary Systems''
	at APS April Meeting 2009 in Denver
\item	Member of Nominating Committee for the APS Topical Group on
	Gravitation Executive Committee 2015
%\item	Public lecture to Astronomical Society of the Palm Beaches, 
%	West Palm Beach, FL, 8/5/2007
%\item	Supervisor of summer internship of high-school 
%	student (Shawn Westerdale), 6/2007
\item	Co-chair of FAU's High Performance Computing  
	governance committee 
\item	Chair Physics Department hiring committee 2014
\item   Member of the College of Science's Promotion \& Tenure committee
\item	Graduate adviser of the Physics Department
\item	Member of the Graduate Qualifying Exam Committee
\item	Webmaster for Physics Department
\item	Organizer of Physics Colloquium, Spring 2014, 2010 and 2007
\item	Organizer of FAUST seminar series, 2007-2011, 2013, 2014
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

% \vspace{0.4in}
% 
% \begin{tabular}{ll}
% {\bf Computer Skills:} & \\ 
%  &  Experience in writing numerical code in C, C++, Fortran \\
%  &  Experience with Cactus and writing Thorns for Cactus\\
%  &  Experience with Linux/Unix system administration \\
% \end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
%\bigskip

{\bf Awards:}

\begin{itemize}
\item	2014 FAU Researcher of the Year Award in the category
	of Associate Professor at FAU
\item	2006 College of Science Researcher of the Year Award in the category
	of Assistant Professor at FAU
\item	1993 Baden-W\"urttemberg Austauschstipendium
%??? \item	Diplom mit Auszeichnung: \\
%	Graduated Summa Cum Laude with highest departmental 
%	honors in physics from Universit\"at Karlsruhe.
%\item	1989 Buchpreis der chemischen Industrie
\end{itemize}


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\bigskip
%%\bigskip
%\clearpage
%
%{\bf References:}
%
%\begin{itemize}
%\item	Bernd Br\"ugmann \\
%	Professor der Physik \\
%	Theoretisch-Physikalisches Institut \\
%	Abbeanum 211\\
%	Friedrich-Schiller-Universit\"at Jena\\
%	07743 Jena, Germany \\
%	{\bf bernd.bruegmann@uni-jena.de}\\
%\item	Pablo Laguna \\
%	Professor of Physics and CRA Director\\
%	Center for Relativistic Astrophysics\\
%	1-63 Boggs Bldg \\
%	Georgia Institute of Technology\\
%	Atlanta, GA 30332 \\ 
%	{\bf plaguna@gatech.edu}\\ 
%\item	\'Eanna \'E. Flanagan\\
%	Professor of Physics and Astronomy \\
%	Center for Radiophysics and Space Research \\
%	606 Space Sciences Building \\
%	Cornell University \\
%	Ithaca, NY 14853 \\
%	{\bf flanagan@astro.cornell.edu}\\ 
%\item	Steven Detweiler \\
%	Professor of Physics \\
%	Department of Physics \\
%	2071 New Physics Building \\
%	University of Florida \\
%	Gainesville, FL 32611 \\
%	{\bf det@phys.ufl.edu}\\ 
%%\item	Abhay Ashtekar \\
%%	Eberly Professor of Physics \\
%%	Institute for Gravitation and the Cosmos \\
%%	316 Whitmore Lab  \\
%%	The Pennsylvania State University \\
%%	University Park, PA 16802 \\
%%	{\bf ashtekar@gravity.psu.edu}\\ 
%%%\item	Saul Teukolsky\\
%%%	Hans Bethe Professor of Physics and Astronomy \\
%%%	Center for Radiophysics and Space Research \\
%%%	Space Sciences Building \\
%%%	Cornell University \\
%%%	Ithaca, NY 14853 \\
%%%	{\bf saul@astro.cornell.edu}\\ 
%\end{itemize}


\end{document}
