\documentclass[11pt]{article}

% Deutsche Umlaute als ASCII Zeichen eingeben:
% ASCII-Codetabellen werden dem Paket inputenc als Option übergeben:
% Linux: latin1, Windows: ansinew, MS-DOS: cp850. 
% Die Abhängigkeit vom Betriebssystem gilt aber nur für den Editor.
% Die LaTeX-Datei wird weiterhin auf jeder Plattform korrekt übersetzt!
\usepackage[latin1]{inputenc}

%\pagestyle{empty}


% see p. 182 of latex book. US letter = 8.5in x 11in.  A4 = 210mm x 297mm
\topmargin      = 0in
\oddsidemargin  = 0in
\evensidemargin = 0in
\textwidth  = 6.5in
\textheight = 9in  % 8,8in
\headheight = 0in
\headsep    = 0in  % 0.2in
%\footskip   = 0in

% no indentation
\parindent=0pt
\parsep=0pt

\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{center}

{\large \bf Wolfgang Tichy}
\medskip

Science \& Engineering Building, Room 444 \\
Physics Department\\
Florida Atlantic University\\
Boca Raton, FL 33431\\

\medskip

Phone: (561) 318-0442 \ \ \ \ \ \ \ \ E-mail: wolf@fau.edu \\
%http://gravity.phys.psu.edu/$\tilde{\ }$wolf \\

\end{center}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip
%\bigskip	

{\bf Professional Preparation:}\\

\begin{tabular}{lll}
Universit\"at Karlsruhe, Karlsruhe, Germany&
Physics		& Diplom 1996\\
Cornell University, Ithaca, NY&
Physics		& Ph.D. 2001\\
Albert-Einstein-Institut, Potsdam, Germany&
General Relativity	& Postdoc 9/2001-9/2002\\
Penn State University, State College, PA&
General Relativity	& Postdoc 9/2002-12/2004\\
\end{tabular}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 
\bigskip
\bigskip

{\bf Appointments:}\\

\begin{tabular}{llll}
Associate  Professor & Physics Department & Florida Atlantic University
&2010-\\
Assistant Professor & Physics Department & Florida Atlantic University
&2004-2010\\
\end{tabular}



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

{\bf Publications closely related to the proposed project:}\\

\underline{W. Tichy},
``Constructing quasi-equilibrium initial data for binary neutron stars
with arbitrary spins'', Phys. Rev. {\bf D86}, 064024, 2012,
arXiv:1209.5336 [gr-qc]
\\

G. Reifenberger and \underline{W. Tichy},
``Alternatives to standard puncture initial data for binary black hole
evolution'', Phys. Rev. {\bf D86}, 064003, 2012,
arXiv:1205.5502 [gr-qc]
\\


\underline{W. Tichy} and P. Marronetti,
``The final mass and spin of black hole mergers'',
Rapid Communication in Phys. Rev. {\bf D 78}, 081501 (2008),
arXiv:0807.2985 [gr-qc]
\\

\underline{W. Tichy} and P. Marronetti,
``Binary black hole mergers: large kicks for generic spin orientations'',
Rapid Communication in Phys. Rev. {\bf D 76}, 061502 (2007),
gr-qc/0703075
\\

B. Br\"ugmann, J.A. Gonzalez, M. Hannam, S. Husa, U. Sperhake
and \underline{W. Tichy},
``Calibration of Moving Puncture Simulations'', 
Phys. Rev. {\bf D 77}, 024027 (2008), gr-qc/0610128
\\


%\clearpage

{\bf Other Notable Publications:}\\

P. Ajith et al., \underline{W. Tichy} [co-author],
``The NINJA-2 catalog of hybrid post-Newtonian/numerical-relativity
waveforms for non-precessing black-hole binaries'',
Class. Quant. Grav. {\bf 29}, 124001 (2012), arXiv:1201.5319 [gr-qc]
\\

\underline{W. Tichy},
``Initial data for binary neutron stars with arbitrary spins '',
Phys. Rev. {\bf D84}, 024041, 2011,
arXiv:1107.1440 [gr-qc] 
\\

\underline{W. Tichy} and P. Marronetti,
``A Simple method to set up low eccentricity initial data for moving
puncture simulations'', Phys. Rev. {\bf D 83}, 024012, 2011,
arXiv:1010.2936v2 [gr-qc]
\\

N. K. Johnson-McDaniel, N. Yunes, \underline{W. Tichy}, and B. J. Owen,
``Conformally curved binary black hole initial data including tidal
deformations and outgoing radiation'',
Phys. Rev. {\bf D 80}, 124039, 2009, arXiv:0907.0891 [gr-qc]
\\

\underline{W. Tichy},
``Long term black hole evolution with the BSSN system
by pseudo-spectral methods'',
Phys. Rev. {\bf D 80}, 104034, 2009, arXiv:0911.0973v2 [gr-qc] 
\\

P. Marronetti, \underline{W. Tichy}, B. Br\"ugmann, J. Gonzalez, 
and U. Sperhake, ``High-spin binary black hole mergers'',
Phys. Rev. {\bf D 77},064010 (2008), arXiv:0709.2160 [gr-qc]
\\

B. J. Kelly, \underline{W. Tichy}, M. Campanelli and B. F. Whiting
``Black hole puncture initial data with realistic gravitational wave content'',
Phys. Rev. {\bf D 76}, 024008 (2007), arXiv:0704.0628 [gr-qc]
\\

B. Br\"ugmann, \underline{W. Tichy} and N. Jansen,
``Numerical simulation of orbiting black holes'',
Phys. Rev. Lett. {\bf 92}, 211101 (2004), gr-qc/0312112


%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip

{\bf Synergistic Activities:}\\

$\bullet$	Co-developed and refined the BAM code for the 
		numerical simulation of the Einstein Equations\\
$\bullet$	Developed the SGRID code for numerical simulations
		by pseudo-spectral methods\\
$\bullet$	Referee for the following journals:
		Physical Review Letters, Physical Review D,
		Classical \& Quantum Gravity

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\bigskip
\bigskip


{\bf Recent Collaborators and Co-Editors:}\\

%M. Ansorg (AEI),
%C. Beetle (FAU),
S. Bernuzzi (U. of Jena),
B. Br\"ugmann (U. of Jena),
%S. Bruenn (FAU),
M. Campanelli (RIT),
S. Detweiler (UFL),
P. Diener (LSU),
\'E. \'E. Flanagan (Cornell),
J. Gonz{\'a}lez (U. Michoacana),
M. Hannam (Univ. of Vienna),
D. Hilditch (U. of Jena),
S. Husa (Univ. of Illes Balears),
%P. Laguna (Georgia Tech),
P. Marronetti (FAU),
B. Kelly (NASA),
N. Johnson-McDaniel (U. of Jena),
%W. Miller (FAU),
B. Owen (PSU),
%G. Sch\"afer (U. of Jena),
U. Sperhake (Barcelona),
M. Thierfelder (U. of Jena),
I. Vega (Guelph),
B. Whiting (UFL),
N. Yunes (MSU),
Y. Zlochower(RIT) 
 \\


\medskip
{\bf Graduate and Postdoctoral Advisers:}\\

B. Br\"ugmann (U. of Jena),
\'E. \'E. Flanagan (Cornell),
Dr. Saul Teukolsky (Cornell)
 \\


\medskip
{\bf Thesis Advisees:}\\

Anastasija Cabolova (FAU),
AmirAli Farokhniaee (FAU),
George Reifenberger (FAU),
Petr Tsatsin (FAU)
 \\

\end{document}

