\documentclass[11pt]{letter}

%%\hyphenation{experience interacting acquired}
%%\parskip 0pt
%%\parindent 0pt
\setlength{\textwidth}{6in}
\setlength{\textheight}{10in}
\setlength{\hoffset}{0.23in}
\setlength{\oddsidemargin}{0in}
\setlength{\topmargin}{0in}
\setlength{\voffset}{0in}
\setlength{\headheight}{0in}
\setlength{\headsep}{0in}
\pagestyle{empty}

\address{Dr.\ Wolfgang Tichy\\
Center for Gravitational Physics and Geometry\\
and Center for Gravitational Wave Physics\\
104 Davey Lab, Box 72 \\
The Pennsylvania State University \\
University Park, PA 16802}

\signature{Wolfgang Tichy}

\begin{document}
\begin{letter}{Dr.\ Roger Mc.\ Neil, Chairman \\
Department of Physics \& Astronomy \\
Louisiana State University \\
202 Nicholson Hall \\
Baton Rouge, LA 70803-4001}


\opening{Dear Prof.\ Mc.\ Neil,}

I wish to apply for the tenure-track faculty position in Computational
Relativity at Louisiana State University. Enclosed you find a curriculum
vitae and a description of my research interests. In addition I have asked
Bernd Br\"ugmann, Pablo Laguna, \'Eanna Flanagan and Abhay Ashtekar to send
you letters of recommendation on my behalf.

Currently I am a postdoc with a joint appointment at both the Center for
Gravitational Wave Physics and the Center for Gravitational Physics and
Geometry at Penn State University. I am working on numerical simulations of
binary black hole systems. I have experience in both the time evolution of
such systems and also in the construction of realistic initial data. Until
September 2002, I was a postdoc at the Albert-Einstein-Institut in Golm,
Germany, where I was mainly working on constructing realistic initial data
by incorporating post-Newtonian information. Before that I was a graduate
student of Professor \'Eanna Flanagan at Cornell University, where I was
working on a broad range of topics including projects in gravitational waves,
post-Newtonian theory, radiation reaction, and semiclassical relativity.

I am very committed to pursuing a career in academia, and I look forward to
hearing from you regarding my application. 
If you wish to discuss my professional and research background
in further detail, please call me at (814) 863-9595 (work) or 
(814) 867-1766 (home).
Thank you for your time and consideration of my application.

\closing{Sincerely,}

\bigskip
%\bigskip 
%\bigskip

\encl{Curriculum vitae\\
%Publication list\\
Description of research interests}


\end{letter}
\end{document}



