
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Publication list, to be included with \input{publist.tex}
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% 

J. von Delft, D. S. Golubev, \underline{W. Tichy} and A. D. Zaikin,
``Parity-Effected Superconductivity in Ultrasmall Metallic Grains'',
Phys. Rev. Lett. {\bf 77}, 3189-3192 (1996), cond-mat/9604072 
\\

\underline{W. Tichy} and \'E. \'E. Flanagan, 
``How unique is the expected stress-energy tensor of a massive scalar
field?'',
Phys. Rev. D {\bf 58}, 124007 (1998), gr-qc/9807015 
\\

\underline{W. Tichy}, \'E. \'E. Flanagan and E. Poisson,
``Can the post-Newtonian gravitational waveform of an inspiraling binary
be improved by solving the energy balance equation numerically?'',
Phys. Rev. D {\bf 61}, 104015 (2000), gr-qc/9912075 
\\

\underline{W. Tichy} and \'E. \'E. Flanagan,
``Angular momentum ambiguities in asymptotically flat spacetimes which 
are perturbations of stationary spacetimes'', 
Class. Quant. Grav. {\bf 18}, 3995 (2001)
\\

\underline{W. Tichy} and \'E. \'E. Flanagan,
``Angular momentum ambiguities in asymptotically flat perturbed
stationary spacetimes'',
Proceedings of the Ninth Marcel Grossmann Meeting on
General Relativity, edited by V.G. Gurzadyan, R.T. Jantzen and R. Ruffini,
World Scientific, Singapore, p. 1622, (2002)
\\

\underline{W. Tichy}, B. Br\"ugmann, M. Campanelli and P. Diener, 
``Binary black hole initial data for numerical general
relativity based on post-Newtonian data'', 
Phys. Rev. {\bf D 67}, 064008 (2003), gr-qc/0207011
\\

\underline{W. Tichy}, B. Br\"ugmann and P. Laguna, 
``Gauge conditions for binary black hole puncture data 
based on an approximate helical Killing vector'', 
Phys. Rev. {\bf D 68}, 064008 (2003), gr-qc/0306020
\\

\underline{W. Tichy} and B. Br\"ugmann,
``Quasi-equilibrium binary black hole sequences for 
puncture data derived from helical Killing vector conditions'', 
Phys. Rev. {\bf D 69}, 024006 (2004), gr-qc/0307027
\\

B. Br\"ugmann, \underline{W. Tichy} and N. Jansen,
``Numerical simulation of orbiting black holes'',
Phys. Rev. Lett. {\bf 92}, 211101 (2004), gr-qc/0312112
\\

M. Ansorg, B. Br\"ugmann and \underline{W. Tichy},
``A single-domain spectral method for black hole puncture data'',
Phys. Rev. {\bf D 70}, 064011 (2004), gr-qc/0404056
\\

N. Yunes, \underline{W. Tichy}, B. J. Owen, and B. Br\"ugmann, 
``Binary black hole initial data from matched asymptotic expansions'',
Phys. Rev. {\bf D 74}, 104011 (2006), gr-qc/0503011.
\\

N. Yunes, and \underline{W. Tichy}, 
``Improved initial data for black hole binaries by asymptotic matching
of post-Newtonian and perturbed black hole solutions'',
Phys. Rev. {\bf D 74}, 064013 (2006), gr-qc/0601046
\\

\underline{W. Tichy}, 
``Black hole evolution with the BSSN system by pseudo-spectral methods'',
Phys. Rev. {\bf D 74}, 084005 (2006), gr-qc/0609087
\\

N. Jansen, B. Br\"ugmann and \underline{W. Tichy},
``Numerical stability of the AA evolution system compared to the ADM and
BSSN systems'', Phys. Rev. {\bf D 74}, 084022 (2006), gr-qc/0310100
\\

B. Br\"ugmann, J.A. Gonzalez, M. Hannam, S. Husa, U. Sperhake
and \underline{W. Tichy},
``Calibration of Moving Puncture Simulations'', gr-qc/0610128
\\

B. Br\"ugmann, J. Gonzalez, M. Hannam, 
S. Husa, P. Marronetti, U. Sperhake, and \underline{W. Tichy},
``Gravitational Wave Signals from Simulations of Black Hole
Dynamics'',
to appear in the Proceedings of the High Performance Computing
in Science and Engineering Workshop. Stuttgart, Germany, (2006)
\\

P. Marronetti, \underline{W. Tichy}, B. Br\"ugmann, J. Gonzalez, M. Hannam, 
S. Husa, and U. Sperhake,
``Binary black holes on a budget: Simulations using workstations'',
Class. Quant. Grav. {\bf 24}, S43-S58 (2007), gr-qc/0701123
\\

\underline{W. Tichy} and P. Marronetti,
``Binary black hole mergers: large kicks for generic spin orientations'',
Rapid Communication in Phys. Rev. {\bf D 76}, 061502 (2007),
gr-qc/0703075
\\

B. J. Kelly, \underline{W. Tichy}, M. Campanelli and B. F. Whiting
``Black hole puncture initial data with realistic gravitational wave content'',
Phys. Rev. {\bf D 74}, 024008 (2007), arXiv:0704.0628 [gr-qc]
\\

P. Marronetti, \underline{W. Tichy}, B. Br\"ugmann, J. Gonzalez, 
and U. Sperhake, ``High-spin binary black hole mergers'',
submitted to Phys. Rev. D, arXiv:0709.2160 [gr-qc]
\\


\underline{W. Tichy} and \'E. \'E. Flanagan,
``Coordinate independent formulation of post-1-Newtonian approximation  
to General Relativity'', 
in preparation 
\\



%  \underline{W. Tichy} and B. Br\"ugmann,
%  ``Properties of a new strongly hyperbolic first order version of 
%    the BSSN system'', 
%  in preparation
% \\
%
%%  \underline{W. Tichy} and \'E. \'E. Flanagan, 
%%  ``Computing the evolution of the Cater constant for scalar radiation from  
%%    a conserved quantity for scalar fields in Kerr spacetime'', 
%%  in preparation 
%% \\

